%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[hidelinks,11pt,a4paper,roman]{moderncv}
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 
\moderncvcolor{blue}     
\renewcommand{\familydefault}{\rmdefault}                           
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by 
\usepackage{multicol}

\usepackage[scale=0.75, top=2cm, bottom=1cm]{geometry}


\name{Richard-Johnson}{Farukh}
\mobile{07495360895}
\email{richard1996johnson@gmail.com}    

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\makecvtitle
\vspace*{-10mm}

\section{Education}
\begin{itemize}
    \item \cventry{2015--2019}{BSc Hons in Computer Science with IE}{University of Manchester}{}{}{}

    \begin{itemize}    
        % \cvdoubleitem{Second year (79\% overall)}{}{Third year (83\% 1\textsuperscript{st} sem.)}{} 
        \cvdoubleitem{Second year (79\% overall)}{}{Third year}{} 
 
        \cvlistdoubleitem{\normalfont{Distributed Computing}}{Advanced Algorithms}
        \cvlistdoubleitem{\normalfont{Machine Learning}}{Advanced Computer Graphics}
        \cvlistdoubleitem{\normalfont{Operating systems}}{The Internet of Things}
        \cvlistdoubleitem{\normalfont{System Architecture}}{Cryptography and Network Security}

    \end{itemize}
        

    %\item \cventry{2010--2015}{Foreign Language School, Lovech, Bulgaria}{Diploma za Sredno Obrazovanie}{}{}{GPA: 5.78/6 (A*AA equivalent)}
\end{itemize}

\section{Experience}
\hfill 
\subsection{Work Experience}
\begin{itemize}
    \item \cventry{2017--2018}{Intern Software Developer}{Team Netsol}{}{}{}
    \begin{itemize}
        \item \normalfont{Worked as a developer on numerous projects within an Agile development team. The role involved maintaining and debugging a Java web application with IntelliJ IDEA and using Git and SVN for version control.}
        \item \normalfont{Developed Bash and Python scripts for automating XML updates, reformatting CSVs and for increasing productivity in day-to-day tasks.}
        \item \normalfont{Was responsible for updating website templates for customers and personalizing the product's features to a provided spec sheet.}
        \item \normalfont{Collaborated on an optimization to speed up deployment to customer sites.}
    \end{itemize}
\end{itemize}

\subsection{Projects}
\begin{itemize}%
\item \textbf{Third Year Project}
  \begin{itemize}%
  \item {I am currently writing software in Python 3 that interprets the movements of tickets on a physical task board from photographs.}
  \item {It uses OpenCV and Numpy to do pixel manipulation, KNN clustering for color grouping, and a CNN classifier for digit recognition. In the backend, it simulates a project tracking service and logs activities.}
  \end{itemize}
\item \textbf{Particle System}
  \begin{itemize}
    \item {Created a particle system in C++ using OpenGL and GLUT, which allowed the customization of particle sources, rendering types, speed, and gravity.}
  \end{itemize}
\item \textbf{FPGA Alarm Clock}
  \begin{itemize}
    \item {For my final project in the Microcontrollers course, I wrote an alarm clock in ARM Assembly which simulated concurrency, and allowed interfacing using a keypad, buzzer, and a display, through interrupts and Supervisor calls.}
  \end{itemize}
\item \textbf{LED Cube}
\begin{itemize}
  \item{At StudentHack IV collaborated on a three dimensional LED cube which operated using an Arduino module. For the project, I wrote algorithms in Java for demonstrating the visualization features of the cube.}
\end{itemize}
\end{itemize}

% \section{Languages}
% \begin{minipage}{\maincolumnwidth}
%   \begin{multicols}{2}
%     \textbf{English}{: Fluent}\\
%     \textbf{Bulgarian}{: Mothertongue}\\
%     \columnbreak \\
%     \textbf{Russian}{: Orally fluent}\\
%     \textbf{Bengali}{: Orally fluent}
%   \end{multicols}
% \end{minipage}
% \vspace*{-\baselineskip}

\section{Interests}
\begin{itemize}
  \item \cvitem{Unix}{Exploring Unix has assisted me in many aspects of my previous job, and I enjoy learning command line shortcuts for otherwise mundane tasks.}
  \item \cvitem{Photography}{My interests in photography and editing sparked my Third Year Project idea, and have been invaluable in helping me understand the image masking aspect of it.}
\end{itemize}
\nocite{*}

\end{document}