%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[hidelinks,11pt,a4paper,roman]{moderncv}
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 
\moderncvcolor{blue}     
\renewcommand{\familydefault}{\rmdefault}                           
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by 
\usepackage{multicol}

\usepackage[scale=0.75, top=2cm, bottom=1cm]{geometry}


\name{Richard-Johnson}{Farukh}
\mobile{07495360895}
\email{richard1996johnson@gmail.com}    

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\makecvtitle

Dear Hiring Manager,
\bigbreak
%\enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname

I write in response to the opening of the Software Development Intern position for 2017. As a second year Computer Science student at the University of Manchester and I am looking to learn new technologies and start a career in software engineering. I believe that as the fastest growing tech travel company in the world, Amadeus provides a constantly evolving work environment and shapes its employees into truly exceptional programmers, which is a reason why I would like to do my placement year at your company. 
\bigbreak
What I can contribute to Amadeus is my skills in solving logical and analytical problems, as well as hard work and dedication to projects I am involved in. This year I am studying machine learning as well as logic and modelling and I am being exposed to a range of software engineering principles and technologies, ranging from unit testing to algorithm complexity and design. 
\bigbreak
Currently I am gaining experience in analyzing requirements, debugging and adding features to an existing Java project called Stendhal. It involves working in a team on set issues and deadlines and has helped me develop my skills in leadership and critical thinking. Working on this program has taught me the importance of writing clean documented code which is easy to modify and the value of maintaining good relationships with my teammates.
\bigbreak
As Amadeus provides IT solutions to virtually all travel companies, it is the core innovator in the industry, and I am excited to be a part of the company's global team and contribute to its success. Thank you for taking your time to review my application.
\bigbreak
Sincerely, \\[2\baselineskip]
Richard-Johnson Farukh

\end{document}


%% end of file `template.tex'.
